A Machine Profile Summary

### 2022-06-13 MachineSummary/MachineSummary.Rmd
Edits to articles and blog posts
changed data time format:aesthetics?

```{r tdstamp}
#get a timestamp
tsstr<- format(Sys.time(), "%Y%m%d%H%M") # tsstr == time stamp string in form YYYYmmddHHMM
cat("Date and Time stamp:",tsstr,"\n")
```

>>>>

```{r tdstamp}
#get a timestamp
tsstr<- format(Sys.time(), "%Y/%m/%d|%H:%M") # tsstr == time stamp string in form YYYYmmddHHMM
cat("Date and Time stamp:",tsstr,"\n")
```
